Reproducible Research in R: A Tutorial on how to Do the Same Thing More Than Once

### 2021-11-22 manuscript.Rmd
add warning

```{r, eval=FALSE}
simulate_data <- function(n, effect_size){
  # Draw n samples from a normal distribution for predictor X
  x <- rnorm(n)
  # Calculate dependent variable Y
  # as a function of population effect size and residual error
  y <- effect_size * x + rnorm(n)
  # Return a data.frame
  data.frame(x = x, y = y)
}
```

>>>>

```{r, eval=FALSE}
simulate_data <- function(n, effect_size){
  warning("This manuscript contains mock results based on simulated data.")
  # Draw n samples from a normal distribution for predictor X
  x <- rnorm(n)
  # Calculate dependent variable Y..
  #.. as a function of population effect size and residual error
  y <- effect_size * x + rnorm(n)
  # Return a data.frame
  data.frame(x = x, y = y)
}
```
